---
title: "RWorksheet_urdas#5"
author: "Cindy Urdas"
date: "2022-11-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.
Course Year	2019 - 2020**\
1st	80\
2nd	75\
3rd	70\
4th	60\


**a.	Plot the data using a bar graph. Write the codes and copy the result.**\
```{r enrollment, echo=FALSE}
Enrollment <-c(80,75,70,60)
barplot(Enrollment,
        main="BS in Computer Science",
        xlab="Course Year",
        ylab="SY2019-2020",
        names.arg = c("1st", "2nd", "3rd", "4th"),
        col="cyan",)
```

b.	Using the same table, label the barchart with Title = ” Enrollment of BS Computer Science horizontal axis = “Curriculum Year” and vertical axis = “number of students”\
```{r, echo=FALSE}
Enrollment <-c(80,75,70,60)
barplot(Enrollment,
        main="Enrollment of BS Computer Science",
        xlab="Curriculum Year",
        ylab="number of students",
        names.arg = c("1st", "2nd", "3rd", "4th"),)
```
**2.	The monthly income of De Jesus family was spent on the following:**\

60% on Food, 10% on electricity, 5% for savings, and 25% for other miscellaneous expenses.\
a.	Create a table for the above scenario. Write the codes and its result.\
```{r percent, echo=FALSE}
percent_spent <- c(60,10,5,25)
barplot(percent_spent,names.arg = c("Food", "Electricity", "Savings", "Miscellaneous"))

```

b.	Plot the data using a pie chart. Add labels, colors and legend. Write the codes and its result.\
```{r percent1, echo=FALSE}
percent_spent <- c(60,10,5,25)
pie(percent_spent)
percent <- pie(percent_spent,
             col = rainbow(length(percent_spent)),
             labels = c(60,10,5,25))

percent1 <- round(percent_spent/sum(percent_spent) * 100, 1)

percent1 <- paste(percent1,"%",sep = "")
pie(percent_spent, main = "The monthly income of De Jesus family was spent on the following:

",col=rainbow(length(percent_spent)),labels = percent1,cex=0.8)

legend(1, c("Food", "Electricity", "Savings", "Miscellaneous"),
       cex = 0.8,fill = rainbow((length(percent_spent))))


```
**3.	Open the mtcars dataset.**\

a.	Create a simple histogram specifically for mpg (miles per gallon) variable. Use $ to select the mpg only. Write the codes and its result.\
```{r, echo=FALSE}
a<-mtcars$mpg
a

a2 <-hist(a, xlab="Miles Per Gallon",
          main="Simple Histogram")

```

b.	Colored histogram with different number of bins. hist(mtcars$mpg, breaks=12, col="red") Note: breaks= controls the number of bins\
```{r, echo=FALSE}
b3 <-hist(a, breaks=12, col="red", xlab="Miles Per Gallon",
              main="Histogram of MPG")
```
c.	Add a Normal Curve
x <- mtcars$mpg
h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon", main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40) yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x) lines(xfit, yfit, col="blue", lwd=2)
Copy the result.

```{r, echo=FALSE}
a<-mtcars$mpg
c3 <-hist(a, breaks=12, col="red", xlab="Miles Per Gallon",
           main="Histogram with Normal Curve")
xfit<-seq(min(a),max(a),length=40)
yfit<-dnorm(xfit,mean=mean(a),sd=sd(a))
yfit <- yfit*diff(c3$mids[1:2])*length(a)
lines(xfit, yfit, col="blue", lwd=2)

```
**4.	Open the iris dataset. Create a subset for each species.**\

a.	Write the codes and its result.
```{r, echo=FALSE}
library(datasets)
str(iris)

sub1 <- subset(iris, Species == "setosa")
sub2 <- subset(iris, Species == "versicolor")
sub3 <- subset(iris, Species == "virginica")

```

b.	Get the mean for every characteristics of each species using colMeans().\ Write the codes and its result.\
Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])\
```{r, echo=FALSE}
sub1 <- subset(iris, Species == "setosa")
setosa <- colMeans(sub1[sapply(sub1,is.numeric)])
setosa

sub2 <- subset(iris, Species == "versicolor")
versicolor <- colMeans(sub2[sapply(sub2,is.numeric)])
versicolor

sub3<- subset(iris, Species == "virginica")
virginica<- colMeans(sub3[sapply(sub3,is.numeric)])
virginica

```
c.	Combine all species by using rbind()\
The table should be look like this:\
```{r, echo=FALSE}
table <- rbind(setosa, versicolor, virginica)
table
```
d.	From the data in 4-c: Create the barplot(). Write the codes and its result.\
```{r, echo=FALSE}
barplot(table, beside = TRUE,
        main = "Iris Data",
        xlab = "Characteristics",
        ylab = "Mean Scores",
        col = c("red","green","blue"))

```

 



 




 



